---
title: "Some Simple SPOOKY Data Analysis"
author: "Cindy Rush"
date: "January 22, 2018"
output:
  pdf_document: default
  html_document: default
---

# Introduction

This files contains some simple analysis of the SPOOKY data.  The goal is to remind ourselves of some of our basic tools for working with text data in `R` and also to practice reproducibility.  You should be able to put this file in the `doc` folder of your `Project 1` repository and it should just run (provided you have `multiplot.R` in the `libs` folder and `spooky.csv` in the `data` folder).  If you open to file from a forked `Week1-GitHub` repo, you should have no trouble running the code directly.

## Setup the libraries
First we want to install and load libraries we need along the way.  Note that the following code is completely reproducible -- you don't need to add any code on your own to make it run.

```{r, message = F, warning = F}
packages.used <- c("ggplot2", "dplyr", "tidytext", "wordcloud", "stringr", "ggridges")

# check packages that need to be installed.
packages.needed <- setdiff(packages.used, intersect(installed.packages()[,1], packages.used))

# install additional packages
if(length(packages.needed) > 0) {
  install.packages(packages.needed, dependencies = TRUE, repos = 'http://cran.us.r-project.org')
}

library(ggplot2)
library(dplyr)
library(tidytext)
library(wordcloud)
library(stringr)
library(ggridges)

source("../libs/multiplot.R")
```

## Read in the data
The following code assumes that the dataset `spooky.csv` lives in a `data` folder (and that we are inside a `docs` folder).

```{r}
spooky <- read.csv('../data/spooky.csv', as.is = TRUE)
```

## An overview of the data structure and content

Let's first remind ourselves of the structure of the data.
```{r}
head(spooky)
summary(spooky)
```

We see from the above that each row of our data contains a unique ID, a single sentence text excerpt, and an abbreviated author name. `HPL` is Lovecraft, `MWS` is Shelly, and `EAP` is Poe.  Here are a few example sentences:

```{r}
spooky$text[1]
spooky$text[13494]
spooky$text[666]
```

We finally note that there are no missing values, and we change author name to be a factor variable, which will help us later on.

```{r}
sum(is.na(spooky))
spooky$author <- as.factor(spooky$author)
```


## An intro to `tidytext`

For my tutorials on Project 1, I will be using `tidytext`.  If this is new to you, here's a textbook that can help: *[Text Mining with R; A Tidy Approach](https://www.tidytextmining.com)*.  It teaches the basic handling of natural language data in `R` using tools from the "tidyverse".  The tidy text format is a table with one token per row, where a token is a word.


### Data Cleaning

We first use the `unnest_tokens()` function to drop all punctuation and transform all words into lower case.  At least for now, the punctuation isn't really important to our analysis -- we want to study the words.  In addition, `tidytext` contains a dictionary of stop words, like "and" or "next", that we will get rid of for our analysis, the idea being that the non-common words (...maybe the SPOOKY words) that the authors use will be more interesting.

```{r}
spooky_wrd <- unnest_tokens(spooky, word, text)
head(spooky_wrd)

head(stop_words)
tail(stop_words)
spooky_wrd <- anti_join(spooky_wrd, stop_words, by = "word")
head(spooky_wrd)
````

### Data Visualization

First we'll do some simple numerical summaries of the data to provide some nice visualizations.

```{r, message = FALSE}
p1 <- ggplot(spooky) +
      geom_bar(aes(author, fill = author)) +
      theme(legend.position = "none")

spooky$sen_length <- str_length(spooky$text)
head(spooky$sen_length)


p2 <- ggplot(spooky) +
      geom_density_ridges(aes(sen_length, author, fill = author)) +
      scale_x_log10() +
      theme(legend.position = "none") +
      labs(x = "Sentence length [# characters]")

spooky_wrd$word_length <- str_length(spooky_wrd$word)
head(spooky_wrd$word_length)

p3 <- ggplot(spooky_wrd) +
      geom_density(aes(word_length, fill = author), bw = 0.05, alpha = 0.3) +
      scale_x_log10() +
      theme(legend.position = "none") +
      labs(x = "Word length [# characters]")

layout <- matrix(c(1, 2, 1, 3), 2, 2, byrow = TRUE)
multiplot(p1, p2, p3, layout = layout)
```


From the above plots we find:

*

*

*


Now we study some of the most common words in the entire data set.  With the below code we plot the fifty most common words in the entire datset. We see that "time", "life", and "night" all appear frequently.

```{r}
words <- names(table(spooky_wrd$word))
freqs <- table(spooky_wrd$word)
head(sort(freqs, decreasing = TRUE))
wordcloud(words, freqs, max.words = 50, color = c("purple4", "red4", "black"))
```
